The Bug Catalog of the Maven Ecosystem

### 2014-02-21 docs/msr.tex
addressed Panos' comments

\maketitle
\begin{abstract}
Examining software ecosystems can provide the research community
with useful information. To examine the ecosystem of
the Maven central repository (approximately 265{\sc gb} of data),
we performed an experiment where we statically analyzed the
repository to detect its software bugs. For our analysis we
used FindBugs, a tool that examines Java bytecode to detect
numerous types of bugs. In this paper we present our dataset. 
\end{abstract}

@@

The dataset construction consisted of two basic steps,
namely: {\it data provenance} and {\it FindBugs results
collection}. Table~\ref{tbl:tools-size} presents some
metrics concerning the tools created for
the process.

@@

{\bf Data Provenance} Initially, we obtained a snapshot
(January 2012) of the Maven repository and handled it
locally to retrieve a list
of all the names of the project versions that existed in
it. In addition, we filtered out projects written in programming
languages other than Java (such as Scala, Groovy, Clojure, etc.)
because FindBugs analyzes only Java bytecode.
Since our construction process took place at the end of 2012,
several versions were released for some of the projects.
Thus, we cross-checked
the local versions with those online\footnote{\url{http://mirrors.ibiblio.org/maven2/}}
and added the missing ones.
The statistic measurements concerning
the repository can be seen in Table~\ref{tbl:repository}
and the distribution of version
count among the selected projects is
presented in Figure~\ref{fig:version-count}.

@@

\begin{figure}[h]
  \begin{center}
    \includegraphics[scale=0.73]{figures/arch.pdf}
  \end{center}
  \caption{The data processing architecture.}
  \label{fig:arch}
\end{figure}

@@

As we mentioned earlier our data was stored in a
Mongo{\sc db} database.
%FindBugs incorporates a priori an ability to perform
%sophisticated queries on bug databases and
%track warnings across multiple versions of code being
%studied.\footnote{\url{http://findbugs.sourceforge.net/manual/datamining.html}}
FindBugs separates software bugs into nine categories (see
Table~\ref{tbl:bug-cat}) and reports {\it bug collections}
that include all the bugs
discovered in a {\sc jar} file. For every registered bug, there are
numerous accompanying features like the class, the method
and the line that the bug was found. Its results, also include
additional information like the number of classes included in
the examined {\sc jar} and others.
FindBugs though,
outputs its results in  {\sc xml} format.
Hence, all the data were
converted to the {\sc json} format
by mapping all {\sc xml} elements to {\sc json} objects.

\begin{table}
\centering
\begin{tabular}{l p{5.0cm}}
 \hline
\verb|version| & The version of the project in the repository. \\
\verb|version_order| & The ordinal version number of the release. \\
\verb|jar_size| & The size of the {\sc jar} file. \\
\verb|dependencies| & List of all dependencies for the project. \\
%\verb|version_list| & A list of all available version's of this project. \\
\verb|group_id| & The group {\sc id} of the project in Maven repository. \\
\verb|jar_filename| & {\sc jar}'s filename. \\
\verb|artifact_id| & The artifact {\sc id} of the project in Maven repository. \\
 \hline
 \end{tabular}
\caption{{\sc jar} metadata description.}
\label{tbl:metadata-description}
\end{table}

As we mentioned in Section~\ref{sec:exp}, our
workers calculated and stored specific metadata together
with the FindBugs results.
Such metadata included its size (in terms of bytecode),
its dependencies
(derived from the {\it pom.xml} file),
and a number that represented the ordinal version
number of the release (see also
Table~\ref{tbl:metadata-description}).
This number was derived from an {\sc xml}
file that accompanies every project in the Maven repository
called {\it maven-metadata.xml}.
The following listing contains a sample document
containing all the above information (note
that the results of FindBugs are too large to
show. To see a complete instance please visit our
{\tt github} repository --- see Section~\ref{sec:conc}):

@@

\section{Dataset Exploitation}
\label{sec:exploit}

@@

\begin{table}[tphp]
    \centering
        \input{bugsperversion.tex}
	\caption{Correlations between version and defects count.}
    \label{tbl:bugsperversion}
\end{table}

@@

Limitations concerning out dataset involve some
{\sc jar}s that were in the initial {\sc jar} list
created during data provenance but when the
FindBugs result collection was performed, they
were not online.

A threat to the internal validity of our experiment could be the false
alarms of the FindBugs tool~\cite{AP10, HP04}.
Specifically, reported security bugs may not
be applicable to an application's typical use context.
For instance, FindBugs could report an {\sc sql}
injection vulnerability~\cite{RL12}
in an application that receives no external input.
In this particular context, this would be a false
positive alarm.

A disadvantage of our dataset is that as projects evolve
the dataset gets older. Also, even if we checked for
new versions before after data provenance and before
the results collection, we did not checked for new
projects added during this time frame.

@@

In this paper, we have presented a dataset that contains
for every {\sc jar} of the Maven central repository,
all the software bug that it contains among with some
other metadata mentioned in Section~\ref{sec:exploit}.
We have also shown how our data can be
used to extract results concerning software evolution.

>>>>

\maketitle
\begin{abstract}
Examining software ecosystems can provide the research community
with useful information. To examine the ecosystem of
the Maven central repository (approximately 265{\sc gb} of data),
we performed an experiment where we statically analyzed the
repository to detect its software bugs. For our analysis we
used FindBugs, a tool that examines Java bytecode to detect
numerous types of bugs. In this paper we present the dataset
that was produced from this experiment.
The dataset contains the metric results that FindBugs reports for
every project version included in the ecosystem. For every
version we also stored specific metadata such as the {\sc jar}'s
size, it's dependencies and others. Finally, we present
how researchers can use our dataset to produce interesting results.
\end{abstract}

@@

The dataset construction consisted of two basic steps,
namely: {\it data cleaning} and {\it FindBugs results
collection}. Table~\ref{tbl:tools-size} presents some
metrics concerning the tools created for
the process.

@@

{\bf Data Cleaning} Initially, we obtained a snapshot
(January 2012) of the Maven repository and handled it
locally to retrieve a list
of all the names of the project versions that existed in
it. In addition, we filtered out projects written in programming
languages other than Java (such as Scala, Groovy, Clojure, etc.)
because FindBugs analyzes only Java bytecode.
Since our construction process took place at the end of 2012,
several versions were released for some of the projects.
Thus, we cross-checked
the local versions with those online\footnote{\url{http://mirrors.ibiblio.org/maven2/}}
and supplemented the missing {\sc jar}s that have been
added to the repository during this period.
The statistic measurements concerning
the repository can be seen in Table~\ref{tbl:repository}
and the distribution of version
count among the selected projects is
presented in Figure~\ref{fig:version-count}.

@@

\begin{figure}[t]
  \begin{center}
    \includegraphics[scale=0.73]{figures/arch.pdf}
  \end{center}
  \caption{The data processing architecture.}
  \label{fig:arch}
\end{figure}

@@

As we mentioned earlier our data was stored in a
Mongo{\sc db} database.
%FindBugs incorporates a priori an ability to perform
%sophisticated queries on bug databases and
%track warnings across multiple versions of code being
%studied.\footnote{\url{http://findbugs.sourceforge.net/manual/datamining.html}}
FindBugs separates software bugs into nine categories (see
Table~\ref{tbl:bug-cat}) and reports {\it bug collections}
that include all the bugs
discovered in a {\sc jar} file. For every registered bug, there are
numerous accompanying features like the class, the method
and the line that the bug was found. FindBug's results, also include
additional information like the number of classes included in
the examined {\sc jar} and others.
FindBugs though,
outputs its results in  {\sc xml} format.
Hence, all the data were
converted to the {\sc json} format
by mapping all {\sc xml} elements to {\sc json} objects.

\begin{table}[b]
\centering
\begin{tabular}{l p{5.0cm}}
 \hline
\verb|version| & The version of the project in the repository. \\
\verb|version_order| & The ordinal version number of the release. \\
\verb|jar_size| & The size of the {\sc jar} file. \\
\verb|dependencies| & List of all dependencies for the project. \\
%\verb|version_list| & A list of all available version's of this project. \\
\verb|group_id| & The group {\sc id} of the project in Maven repository. \\
\verb|jar_filename| & {\sc jar}'s filename. \\
\verb|artifact_id| & The artifact {\sc id} of the project in Maven repository. \\
 \hline
 \end{tabular}
\caption{{\sc jar} metadata description.}
\label{tbl:metadata-description}
\end{table}

As we mentioned in Section~\ref{sec:exp}, our
workers calculated and stored specific metadata together
with the FindBugs results.
Such metadata included the {\sc jar}'s size (in terms of bytecode),
its dependencies
(derived from the {\it pom.xml} file),
and a number that represented the ordinal version
number of the release (see also
Table~\ref{tbl:metadata-description}).
This number was derived from an {\sc xml}
file that accompanies every project in the Maven repository
called {\it maven-metadata.xml}.
The following listing shows the format of the
information we collected (note
that the results of FindBugs are too large to
show. To see a complete instance please visit our
GitHub repository --- see Section~\ref{sec:conc}):

@@

\section{Harnessing Our Dataset}
\label{sec:exploit}

@@

\begin{table}[b]
    \centering
        \input{bugsperversion.tex}
	\caption{Correlations between version and defects count.}
    \label{tbl:bugsperversion}
\end{table}

@@

Limitations concerning out dataset involve some
{\sc jar}s that were in the initial {\sc jar} list
created during data cleaning but when the
FindBugs result collection was performed, they
were not online.

A threat to the internal validity of our experiment could be the false
alarms of the FindBugs tool~\cite{AP10}.
Specifically, reported security bugs may not
be applicable to an application's typical use context.
For instance, FindBugs could report an {\sc sql}
injection vulnerability
in an application that receives no external input.
In this particular context, this would be a false
positive alarm.

A disadvantage of our dataset is that as projects evolve
the dataset gets older. Also, even if we checked for
new versions before data cleaning and before
the results collection, we did not checked for new
projects added during this time frame.

@@

In this paper, we have presented a dataset that contains
for every {\sc jar} of the Maven central repository,
all the software bugs that it contains among with some
other metadata mentioned in Section~\ref{sec:exploit}.
We have also shown how our data can be
used to extract results concerning software evolution.
